---
title: "EmpowerX"
date: "(`r Sys.Date()`)"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    theme: yeti
    source_code: embed
runtime: shiny
---

<!-- v1.0.0
Github repo: https://github.com/rafaefarrukh/EmpowerX 
Read README.md for details such as code notation and data files.
-->

```{r Setup}

# Libraries ----
library(flexdashboard); library(shiny); library(shinyWidgets); library(tidyverse); library(DT); library(lubridate); library(rhandsontable)

# Data ----

## Courses
courses <- read.csv("data/courses_22.csv")
names(courses) <- c("Department", "Code", "Title", "Credits", "Details", "Prerequisite", "Crosslisted Code")

## Programs
programs <- read.csv("data/programs_22.csv")
names(programs) <- c("Program", "nature", "Details", "Requirements", "Course Categories", "Core Courses", "Elective Courses", "Total Credits", "Core Credits", "Elective Credits", "Total Courses", "Core Courses", "Elective Courses")

## Semester lengths (to be changed)
SPRING <- 1:6; SUMMER <- 7:8; FALL <- 9:12; WINTER <- 0

## Grading system
grades <- data.frame(
    Grades = c("A", "A-", "B+", "B", "B-", "C+", "C", "C-", "D+", "D", "F", "NS", "W", "AW", "AU", "I", "T"),
    GPA = c("4.0", "3.7", "3.3", "3.0", "2.7", "2.3", "2.0", "1.7", "1.3", "1.0", "0", "0", "", "", "", "", ""),
    Percentage = c("93 - 100", "90 - 92", "87 - 89", "83 - 86", "80 - 82", "77 - 79", "73 - 76", "70 - 72", "67 - 69", "60 - 66", "1 - 59", "0", "", "", "", "", ""),
    Meaning = c("Superior", "", "Good", "", "", "Satisfactory", "", "", "Passing", "", "Failing", "Did not show up in class", "Officialy withdrawn", "Administrative Withdrawel/Dismissal", "Audit/Listener Status", "Incomplte", "Transfered credit"))

for (i in 1:12) {assign(grades[i,1], as.numeric(grades[i,2]))}
None <- NA; W <- NA; AW <- NA; AU <- NA; I <- NA; T <- NA

# Functions ----

## Extract info from "programs" based on program name and nature
## Used in: UP/SP/Details UP/SP/Requirements UP/SP/Credits_and_Courses UP/SP/Core UP/SP/Elective UP/SP/Course_Categories YD/C/Courses YD/O/Distribution

get_program <- function(input, output, nature) {
    
    # input = name of program
    # output = {1,2,3...13}; each number represents column of program and the info in it
    # nature = {degree, major, minor, specialization, certification}
    
    temp <- data.frame(str_split(as.character(
        filter(programs[output], programs[1] == input, programs[2] == nature)), "\n"))
    
    names(temp) <- paste0(names(programs[output]))
    
    return(temp)
}

## Calculate total number of credits based on course codes
## Used in: YD/D/General YD/D/Courses YD/D/Transfer YD/D/Elective YD/S/Edit
get_credits <- function(input) {sum(as.numeric(unlist(filter(courses[4], courses$Code %in% input))), na.rm = TRUE)}

```

<!------------------------------------------------------------------------------------------------->

# Home {data-orientation="rows"}

## row {data-height=100}

### {}

<center> <font size="10"> **EmpowerX** </font> </center>

## row {data-height=900}

### About {data-width=500}

<center>

<H4> <font color = "red"> **DISCLAIMER: EMPOWERX IS NOT AN OFFICIAL SERVICE OFFERED BY FCCU. AS SUCH THE INFORMATION PRESENT HERE MAY NOT BE FULLY UP TO DATE WITH FCCU AND ITS POLICIES.** </font> </H4>

<br> <hr> <br>

<H4> **LIMITATIONS AND ISSUES** </H4>

</center>

EmpowerX relies on free tools to make itself accessible online, as a result it is **extremely slow**. So kindly be patient when using empowerX. 

Alternatively, if you have any experience with R programming language, you can **download** empowerX and run it locally from your device. The github repo can be found here: https://github.com/rafaefarrukh/EmpowerX

If you want to use this service to track your degree, remember to **export your data before exiting**. EmpowerX blanks out after 10 minutes of inactivity and does not store your data. So if you do not save your data it will be lost and you will have to re enter it.

Currently, empowerX only supports upto **8 regular semesters**. Students who are taking additional semesters may not be able to track their degree properly.

EmpowerX follows the **2022 - 2023 course catalogue**. Different catalogues may have different details, eg. different credit requirement for graduation. Students not following the 2022 - 2023 catalogue must check for differences between their catalogue and the 2022 - 2023 catalogue.

*EmpowerX is a work in progress website and the limitations and issues above are being worked on. But implementing them will take time.*

<br> <hr> <br>

<center> <H4> **CONTACT** </H4> </center>

For any queries, complaints or/and suggestions, contact me at [261936352\@formanite.fccollege.edu.pk](mailto:261936352@formanite.fccollege.edu.pk){.email}

### Services offered by EmpowerX {data-width=500}

<H4> **Undergraduate Program** </H4>

**Details:** A presentation which explains details regarding the undergraduate degree.

**Search Courses:** View the 850+ courses offered by FCCU in an easy to view format.

**Search Programs:** View the 50+ programs (majors, minors, specializations and certifications) offered by FCCU in an easy to understand format.

<br> <hr> <br>

<H4> **Your Degree** </H4>

**Details:** Enter your basic information such as program details and elective courses. This is used to evaluate information in other parts. You can change these details to create *what if* scenarios as well. 

**Semesters:** Enter the courses you have taken or plan on taking and their grades. This is used to evaluate information in other parts. You can use this to plan out your degree in advance. Note that this part is slightly glitchy and may not show all the columns properly. If this happens, click the columns which are present.

**Courses:** View the courses that are required for your graduation. This part is evaluated from the other parts. You can filter by requirement and by semesters, allowing you to quickly audit your degree. You can use this along with the other parts to create *what if* scenarios, such as "if I turn my minor into a major, will I be able to complete the courses in time?"

**Overview:** View summary statistics regarding your degree. The table shows your credit and CGPA distribution according to semesters and requirements. It can be a bit difficult to understand at first, but it allows you to view 4 years worth of information in a single table. Note that this part is a bit slow and takes a few seconds to load/refresh. 

<!------------------------------------------------------------------------------------------------->

# Degree Details {.tabset data-navmenu="Undergraduate Programs"}

```{r UP/DD}

tags$iframe(style="height:100%; width:100%; scrolling=yes", src="data/degree_details.pdf")

```

<!------------------------------------------------------------------------------------------------->

# Search Courses {data-navmenu="Undergraduate Programs"}

## column {.sidebar data-width="250"}

### Filter

Select the departments whose courses you want to see. Similarly, select the credits to view courses of those credits.

If you want to search using a keyword, use the search bar on the top right of the table. 

<br>

```{r UP/SC/Filter}

pickerInput(
    inputId = "dept", label = "Department", 
    choices = sort(unique(courses[,1])),
    selected = sort(unique(courses[,1])),
    options = pickerOptions(actionsBox = TRUE, selectedTextFormat = "count > 3"),
    multiple = TRUE, width = "100%"
)

br()

pickerInput(
    inputId = "cr", label = "Credits",
    choices = c("x", sort(as.numeric(unique(courses[,4])))),
    selected = c("x", sort(as.numeric(unique(courses[,4])))),
    options = pickerOptions(actionsBox = TRUE, selectedTextFormat = "count > 3"),
    multiple = TRUE, width = "100%"
)

```

## column {data-width="750"}

### {}

```{r UP/SC/}

renderDT(datatable(
    courses %>% filter(courses[,1] %in% input$dept, courses[,4] %in% input$cr),
    rownames = FALSE, 
    extensions = 'Responsive',
    options = list(
        pageLength = "100",
        scrollY = "200px",
        columnDefs = list(
            list(width = '5pc', targets = c(0,3)),
            list(width = '7pc', targets = c(1,5,6)),
            list(width = '10pc', targets = c(2)),
            list(width = '64pc', targets = c(0)),
            list(className = 'dt-center', targets = c(0,1,3,6))))) %>%
        formatStyle(c('Department','Code'), fontWeight = 'bold')
)

```

<!------------------------------------------------------------------------------------------------->

# Search Programs {data-navmenu="Undergraduate Programs"}

## column {.sidebar data-width="250"}

### Search

Choose a program below to see its details.

Note that only one program will be showed at a time.

<br>

```{r UP/SP/Search}

selectInput(
    inputId = "dg", label = "Degrees",
    choices = c("None", sort(programs[which(programs[,2] == "degree"),1])), selected = "None"
)

selectInput(
    inputId = "ma", label = "Majors",
    choices = c("None", sort(programs[which(programs[,2] == "major"),1])), selected = "None"
)

selectInput(
    inputId = "mi", label = "Minors",
    choices = c("None", sort(programs[which(programs[,2] == "minor"),1])), selected = "None"
)

selectInput(
    inputId = "sp", label = "Specializations",
    choices = c("None", sort(programs[which(programs[,2] == "specialization"),1])), selected = "None"
)

selectInput(
    inputId = "ct", label = "Certifications",
    choices = c("None", sort(programs[which(programs[,2] == "certification"),1])), selected = "None"
)

actionButton(inputId = "deselect_up_sp_search", label = "Reset", width = "100%")

observeEvent(input$deselect_up_sp_search, {
    updateSelectInput(inputId = "dg", selected = "None")
    updateSelectInput(inputId = "ma", selected = "None")
    updateSelectInput(inputId = "mi", selected = "None")
    updateSelectInput(inputId = "sp", selected = "None")
    updateSelectInput(inputId = "ct", selected = "None")
})

```

## column {data-width="350"}

### Details {data-height="450"}

```{r UP/SP/Details}

renderTable(
    if (input$dg != "None") {get_program(input$dg, 3, "degree")} else
    if (input$ma != "None") {get_program(input$ma, 3, "major")} else
    if (input$mi != "None") {get_program(input$mi, 3, "minor")} else
    if (input$sp != "None") {get_program(input$sp, 3, "specialization")} else
    if (input$ct != "None") {get_program(input$ct, 3, "certification")},
    colnames = FALSE, rownames = FALSE, striped = TRUE, hover = TRUE
)

```

### Requirements {data-height="450"}

```{r UP/SP/Requirements}

renderTable(
    if (input$dg != "None") {get_program(input$dg, 4, "degree")} else
    if (input$ma != "None") {get_program(input$ma, 4, "major")} else
    if (input$mi != "None") {get_program(input$mi, 4, "minor")} else
    if (input$sp != "None") {get_program(input$sp, 4, "specialization")} else
    if (input$ct != "None") {get_program(input$ct, 4, "certification")},
    colnames = FALSE, rownames = FALSE, striped = TRUE, hover = TRUE
)

```

### Credits and Courses {data-height="100"}

```{r UP/SP/Credits_and_Courses}

renderTable(
    if (input$dg != "None") {get_program(input$dg, 8:13, "degree")} else
    if (input$ma != "None") {get_program(input$ma, 8:13, "major")} else
    if (input$mi != "None") {get_program(input$mi, 8:13, "minor")} else
    if (input$sp != "None") {get_program(input$sp, 8:13, "specialization")} else
    if (input$ct != "None") {get_program(input$ct, 8:13, "certification")},
    rownames = FALSE, striped = TRUE, hover = TRUE
)

```

## column {.tabset data-width="350"}

### Core Courses

```{r UP/SP/Core}

renderTable(
    if (input$dg != "None") {filter(courses[c(2:4,6:7)], courses$Code %in% unlist(get_program(input$dg, 6, "degree")))} else
    if (input$ma != "None") {filter(courses[c(2:4,6:7)], courses$Code %in% unlist(get_program(input$ma, 6, "major")))} else
    if (input$mi != "None") {filter(courses[c(2:4,6:7)], courses$Code %in% unlist(get_program(input$mi, 6, "minor")))} else
    if (input$sp != "None") {filter(courses[c(2:4,6:7)], courses$Code %in% unlist(get_program(input$sp, 6, "specialization")))} else
    if (input$ct != "None") {filter(courses[c(2:4,6:7)], courses$Code %in% unlist(get_program(input$ct, 6, "certification")))},
    rownames = FALSE, striped = TRUE, hover = TRUE
)

```

### Elective Courses

```{r UP/SP/Elective}

renderTable(
    if (input$dg != "None") {filter(courses[c(2:4,6:7)], courses$Code %in% unlist(get_program(input$dg, 7, "degree")))} else
    if (input$ma != "None") {filter(courses[c(2:4,6:7)], courses$Code %in% unlist(get_program(input$ma, 7, "major")))} else
    if (input$mi != "None") {filter(courses[c(2:4,6:7)], courses$Code %in% unlist(get_program(input$mi, 7, "minor")))} else
    if (input$sp != "None") {filter(courses[c(2:4,6:7)], courses$Code %in% unlist(get_program(input$sp, 7, "specialization")))} else
    if (input$ct != "None") {filter(courses[c(2:4,6:7)], courses$Code %in% unlist(get_program(input$ct, 7, "certification")))},
    rownames = FALSE, striped = TRUE, hover = TRUE
)

```

### Course Categories (if required)

```{r UP/SP/Course_Categories}

renderTable(
    if (input$dg != "None") {get_program(input$dg, 5, "degree")} else
    if (input$ma != "None") {get_program(input$ma, 5, "major")} else
    if (input$mi != "None") {get_program(input$mi, 5, "minor")} else
    if (input$sp != "None") {get_program(input$sp, 5, "specialization")} else
    if (input$ct != "None") {get_program(input$ct, 5, "certification")},
    colnames = FALSE, rownames = FALSE, striped = TRUE, hover = TRUE
)

```

<!------------------------------------------------------------------------------------------------->

# Details {data-navmenu="Your Degree"}

## column {data-width="250"}

### Export and Import Data {data-height="300"}

```{r YD/D/Export_Import}

renderUI(verticalLayout(
    renderUI(downloadButton(outputId = "export", label = "Export your data")), br(),
    fileInput(inputId = "import", label = "", accept = ".csv", width = "100%", buttonLabel = "Import"),
    actionButton(inputId = "import_multiple", label = "Click after importing data to refresh EmpowerX", width = "100%")
    ))

# export
output$export <- downloadHandler(
    filename = function() {paste0('your_degree-', Sys.Date(), '.csv', sep='')}, 
    content = function(con) {write.csv(as.data.frame(export()), con, row.names = FALSE)})

export <- reactive({
    
    temp <- data.frame(rep(NA, 20))
    
    temp[1,1] <- as.character(input$yd_yr); temp[2,1] <- as.character(input$yd_sem)
    
    temp[1:6, 2] <- as.character(c(input$ma1, input$ma2, input$mi1, input$mi2, input$sp1, input$sp2))
    
    temp[,3] <- c(as.character(input$ma1e), rep(NA, 20 - length(as.character(input$ma1e))))
    temp[,4] <- c(as.character(input$ma2e), rep(NA, 20 - length(as.character(input$ma2e))))
    temp[,5] <- c(as.character(input$mi1e), rep(NA, 20 - length(as.character(input$mi1e))))
    temp[,6] <- c(as.character(input$mi2e), rep(NA, 20 - length(as.character(input$mi2e))))
    temp[,7] <- c(as.character(input$sp1e), rep(NA, 20 - length(as.character(input$sp1e))))
    temp[,8] <- c(as.character(input$sp2e), rep(NA, 20 - length(as.character(input$sp2e))))
    
    temp[,9] <- c(as.character(input$ged1), rep(NA, 20 - length(as.character(input$ged1))))
    temp[1:2,10] <- c(as.character(input$ged2), rep(NA, 2 - length(as.character(input$ged2))))
    temp[3:4,10] <- c(as.character(input$ged3), rep(NA, 2 - length(as.character(input$ged3))))
    temp[5:6,10] <- c(as.character(input$ged4), rep(NA, 2 - length(as.character(input$ged4))))
    temp[7,10] <- c(as.character(input$ged5))
    
    temp[,11] <- c(as.character(input$frel), rep(NA, 20 - length(as.character(input$frel))))
    
    temp[,12] <- c(as.character(input$s0.0), rep(NA, 20 - length(as.character(input$s0.0))))
    
    temp[1:7,13:15] <- as.data.frame(s1.0()); temp[8:10,13:15] <- as.data.frame(s1.5())
    temp[1:7,16:18] <- as.data.frame(s2.0()); temp[8:10,16:18] <- as.data.frame(s2.5())
    temp[1:7,19:21] <- as.data.frame(s3.0()); temp[8:10,19:21] <- as.data.frame(s3.5())
    temp[1:7,22:24] <- as.data.frame(s4.0()); temp[8:10,22:24] <- as.data.frame(s4.5())
    temp[1:7,25:27] <- as.data.frame(s5.0()); temp[8:10,25:27] <- as.data.frame(s5.5())
    temp[1:7,28:30] <- as.data.frame(s6.0()); temp[8:10,28:30] <- as.data.frame(s6.5())
    temp[1:7,31:33] <- as.data.frame(s7.0()); temp[8:10,31:33] <- as.data.frame(s7.5())
    temp[1:7,34:36] <- as.data.frame(s8.0()); temp[8:10,34:36] <- as.data.frame(s8.5())
    
    return(temp)
})

# import
import <- reactive(export())

import <- eventReactive(input$import, {read.csv(input$import$datapath)})

observeEvent(input$import, {
    
    updateSelectInput(inputId = "yd_yr", selected = as.numeric(import()[1,1]))
    updateSelectInput(inputId = "yd_sem", selected = as.character(import()[2,1]))
    
    updateSelectInput(inputId = "ma1", selected = as.character(import()[1,2]))
    updateSelectInput(inputId = "ma2", selected = as.character(import()[2,2]))
    updateSelectInput(inputId = "mi1", selected = as.character(import()[3,2]))
    updateSelectInput(inputId = "mi2", selected = as.character(import()[4,2]))
    updateSelectInput(inputId = "sp1", selected = as.character(import()[5,2]))
    updateSelectInput(inputId = "sp2", selected = as.character(import()[6,2]))
    
    updateSelectInput(inputId = "ged2", selected = as.character(import()[1:2,10]))
    updateSelectInput(inputId = "ged3", selected = as.character(import()[3:4,10]))
    updateSelectInput(inputId = "ged4", selected = as.character(import()[5:6,10]))
    updateSelectInput(inputId = "ged5", selected = as.character(import()[7,10]))

})

observeEvent(input$import_multiple, {
    
    updateSelectInput(inputId = "ma1e", selected = as.character(import()[,3]))
    updateSelectInput(inputId = "ma2e", selected = as.character(import()[,4]))
    updateSelectInput(inputId = "mi1e", selected = as.character(import()[,5]))
    updateSelectInput(inputId = "mi2e", selected = as.character(import()[,6]))
    updateSelectInput(inputId = "sp1e", selected = as.character(import()[,7]))
    updateSelectInput(inputId = "sp2e", selected = as.character(import()[,8]))
    
    updateSelectInput(inputId = "ged1", selected = as.character(import()[,9]))
    updateSelectInput(inputId = "frel", selected = as.character(import()[,11]))
    updateSelectInput(inputId = "s0.0", selected = as.character(import()[,12]))
    
    s1.0(as.data.frame(import()[1:7,13:15])); s1.5(as.data.frame(import()[8:10,13:15]))
    s2.0(as.data.frame(import()[1:7,16:18])); s2.5(as.data.frame(import()[8:10,16:18]))
    s3.0(as.data.frame(import()[1:7,19:21])); s3.5(as.data.frame(import()[8:10,19:21]))
    s4.0(as.data.frame(import()[1:7,22:24])); s4.5(as.data.frame(import()[8:10,22:24]))
    s5.0(as.data.frame(import()[1:7,25:27])); s5.5(as.data.frame(import()[8:10,25:27]))
    s6.0(as.data.frame(import()[1:7,28:30])); s6.5(as.data.frame(import()[8:10,28:30]))
    s7.0(as.data.frame(import()[1:7,31:33])); s7.5(as.data.frame(import()[8:10,31:33]))
    s8.0(as.data.frame(import()[1:7,34:36])); s8.5(as.data.frame(import()[8:10,34:36]))
    
})

```

### Details {data-height="700"}

All students are required to study 15 courses of General Education. Some of these are compulsory and have already been selected. However, there are some exceptions,

-   if your FEAT maths score is good, you are exempt from MATH 100. Instead you have to study another MATH course. Alternatively, if your FEAT maths score is very low, you will have to study MATH 095.

-   if your FEAT English score is very low, you will have to study IEAP courses as well.

Consult with N block to confirm course exemption or addition.

You may have to take free elective courses to reach your credit requirement.

## column {data-width="250"}

### Degree Details

```{r YD/D/Details}

selectInput(
    inputId = "yd_yr", label = "Admission Year",
    choices = 2000:format(Sys.Date(), "%Y"), selected = format(Sys.Date(), "%Y"),
    width = "100%"
)

selectInput(
    inputId = "yd_sem", label = "Admission Year",
    choices = c("FALL", "SPRING"), selected = "FALL",
    width = "100%"
)

br(); hr(); br() # space

selectInput(
    inputId = "ma1", label = "Major 1",
    choices = c("None", sort(programs[which(programs[,2] == "major"),1])), selected = "None",
    width = "100%"
)

selectInput(
    inputId = "ma2", label = "Major 2",
    choices = c("None", sort(programs[which(programs[,2] == "major"),1])), selected = "None",
    width = "100%"
)

selectInput(
    inputId = "mi1", label = "Minor 1", 
    choices = c("None", sort(programs[which(programs[,2] == "minor"),1])), selected = "None",
    width = "100%"
)

selectInput(
    inputId = "mi2", label = "Minor 2",
    choices = c("None", sort(programs[which(programs[,2] == "minor"),1])), selected = "None",
    width = "100%"
)

selectInput(
    inputId = "sp1", label = "Specialization 1",
    choices = c("None", sort(programs[which(programs[,2] == "specialization"),1])), selected = "None",
    width = "100%"
)

selectInput(
    inputId = "sp2", label = "Specialization 2",
    choices = c("None", sort(programs[which(programs[,2] == "specialization"),1])), selected = "None",
    width = "100%"
)

actionButton(inputId = "deselect_yd_d_details", label = "Reset")

observeEvent(input$deselect_yd_d_details, {
    updateVarSelectInput(inputId = "ma1", selected = "None")
    updateVarSelectInput(inputId = "ma2", selected = "None")
    updateVarSelectInput(inputId = "mi1", selected = "None")
    updateVarSelectInput(inputId = "mi2", selected = "None")
    updateVarSelectInput(inputId = "sp1", selected = "None")
    updateVarSelectInput(inputId = "sp2", selected = "None")
})

```

## column {data-width="250"}

###  {data-height="700"}

```{r YD/D/General}

renderUI(verticalLayout(
    renderText("Choose General Education Courses"), br(),

    selectizeInput(
        inputId = "ged1", label = "Compulsory Courses",
        options = list(maxItems = 8), 
        choices = sort(unique(courses[,2])),
        selected = c("UNIV 100", "WRCM 101", "WRCM 102", "PKST 101", "ISLM 101", "URDU 101", "MATH 100", "CSCS 100"),
        multiple = TRUE, width = "100%"
        ),
    
    selectizeInput(
        inputId = "ged2", label = "2 Science Lab Courses",
        options = list(maxItems = 2),
        choices = arrange(filter(courses[2], 
                                 courses$Department %in% c("BIOL", "CHEM", "PHYS"),
                                 courses$Credits %in% c(4))),
        selected = NA, 
        multiple = TRUE, width = "100%"
        ),
    
    selectizeInput(
        inputId = "ged3", label = "2 Social Science Courses",
        options = list(maxItems = 2),
        choices = arrange(filter(courses[2], 
                                 courses$Department %in% c("BUSN", "ECON", "EDUC", "GEOG", "PLSC", "PSYC", "SOCL", "CRIM"),
                                 courses$Credits %in% c(3,4))),
        selected = NA, 
        multiple = TRUE, width = "100%"
        ),
    
    selectizeInput(
        inputId = "ged4", label = "2 Humanities Courses",
        options = list(maxItems = 2),
        choices = arrange(filter(courses[2], 
                                 courses$Department %in% c("ENGL", "LING", "HIST", "MCOM", "PHIL", "ISLM", "CRST", "URDU", "FREN", "GRMN", "KORN", "CHIN"),
                                 courses$Credits %in% c(3,4))),
        selected = NA, 
        multiple = TRUE, width = "100%"
    ),
    
    selectizeInput(
        inputId = "ged5", label = "1 Course from any Domain",
        options = list(maxItems = 1),
        choices = c("PHIL 221", arrange(filter(courses[2], 
                                               courses$Department %in% c("CSCS", "COMP", "MATH", "STAT", "BIOL", "BIOT", "ENVR", "CHEM", "PHYS"),
                                               courses$Credits %in% c(3,4)))),
        selected = NA, 
        multiple = FALSE,  width = "100%"
    ),
    
    renderText(paste("Number of Credits = ", get_credits(ged()))), br(), hr(), br(),
    renderText("Choose Transfer Courses"),
    
    selectInput(inputId = "s0.0", label = "", choices = sort(unique(courses[,2])), selected = NA, multiple = TRUE,  width = "100%"),
    
    renderText(paste("Number of Credits = ", get_credits(input$s0.0)))

))

ged <- reactive(rbind(input$ged1, input$ged2, input$ged3, input$ged4, input$ged5))

```

## column {data-width="250"}

### Choose Free Elective Courses {data-height="300"}

```{r YD/D/Elective}

renderUI(verticalLayout(
    
    selectInput(inputId = "frel", label = "Free Electives", choices = sort(unique(courses[,2])), selected = NA, multiple = TRUE, width = "100%"),
    
    renderText(paste("Number of Credits = ", get_credits(input$frel))), br(), hr(), br(),
    
    # ma1e
    conditionalPanel(
        condition = "input.ma1 != 'None'",
        renderUI({
            if (input$ma1 != "None") {if (as.numeric(get_program(input$ma1, 10, "major")) == 0) {"No Elective Courses for Major 1"} else {
                selectInput(
                    inputId = "ma1e", label = "Major 1 Elective Courses",
                    choices = filter(courses[2], courses$Code %in% unlist(get_program(input$ma1, 7, "major"))), selected = NA,
                    multiple = TRUE, width = "100%"
                    )}}}),
        renderText(
            if (input$ma1 != "None") {
                if (as.numeric(get_program(input$ma1, 10, "major")) == 0) {NULL} else
                    {paste("Number of Credits =", get_credits(input$ma1e), "/", get_program(input$ma1, 10, "major"))}}), br()
        ),
    
    # ma2e
    conditionalPanel(
        condition = "input.ma2 != 'None'",
        renderUI({
            if (input$ma2 != "None") {if (as.numeric(get_program(input$ma2, 10, "major")) == 0) {"No Elective Courses for Major 2"} else {
                selectInput(
                    inputId = "ma2e", label = "Major 2 Elective Courses",
                    choices = filter(courses[2], courses$Code %in% unlist(get_program(input$ma2, 7, "major"))), selected = NA,
                    multiple = TRUE, width = "100%"
                    )}}}),
        renderText(
            if (input$ma2 != "None") {
                if (as.numeric(get_program(input$ma2, 10, "major")) == 0) {NULL} else
                    {paste("Number of Credits =", get_credits(input$ma2e), "/", get_program(input$ma2, 10, "major"))}}), br()
        ),
    
    # mi1e
    conditionalPanel(
        condition = "input.mi1 != 'None'",
        renderUI({
            if (input$mi1 != "None") {if (as.numeric(get_program(input$mi1, 10, "minor")) == 0) {"No Elective Courses for Minor 1"} else {
                selectInput(
                    inputId = "mi1e", label = "Minor 1 Elective Courses",
                    choices = filter(courses[2], courses$Code %in% unlist(get_program(input$mi1, 7, "minor"))), selected = NA, 
                    multiple = TRUE, width = "100%"
                    )}}}),
        renderText(
            if (input$mi1 != "None") {
                if (as.numeric(get_program(input$mi1, 10, "minor")) == 0) {NULL} else
                    {paste("Number of Credits =", get_credits(input$mi1e), "/", get_program(input$mi1, 10, "minor"))}}), br()
        ),
    
    # mi2e
    conditionalPanel(
        condition = "input.mi2 != 'None'",
        renderUI({
            if (input$mi2 != "None") {if (as.numeric(get_program(input$mi2, 10, "minor")) == 0) {"No Elective Courses for Minor 1"} else {
                selectInput(
                    inputId = "mi2e", label = "Minor 2 Elective Courses", 
                    choices = filter(courses[2], courses$Code %in% unlist(get_program(input$mi2, 7, "minor"))), selected = NA,
                    multiple = TRUE, width = "100%"
                    )}}}),
        renderText(
            if (input$mi2 != "None") {
                if (as.numeric(get_program(input$mi2, 10, "minor")) == 0) {NULL} else
                    {paste("Number of Credits =", get_credits(input$mi2e), "/", get_program(input$mi2, 10, "minor"))}}), br()
        ),
    
    # sp1e
    conditionalPanel(
        condition = "input.sp1 != 'None'",
        renderUI({
            if (input$sp1 != "None") {if (as.numeric(get_program(input$sp1, 10, "specialization")) == 0)  {"No Elective Courses for Specialization 1"} else {
                selectInput(
                    inputId = "sp1e", label = "specialization 1 Elective Courses",
                    choices = filter(courses[2], courses$Code %in% unlist(get_program(input$sp1, 7, "specialization"))), selected = NA,
                    multiple = TRUE, width = "100%"
                    )}}}),
        renderText(
            if (input$sp1 != "None") {
                if (as.numeric(get_program(input$sp1, 10, "specialization")) == 0) {NULL} else
                    {paste("Number of Credits =", get_credits(input$sp1e), "/", get_program(input$sp1, 10, "specialization"))}}), br()
        ), br(),
    
    # sp2e
    conditionalPanel(
        condition = "input.sp2 != 'None'",
        renderUI({
            if (input$sp2 != "None") {if (as.numeric(get_program(input$sp2, 10, "specialization")) == 0) {"No Elective Courses for specialization 1"} else {
                selectInput(
                    inputId = "sp2e", label = "Specialization 2 Elective Courses",
                    choices = filter(courses[2], courses$Code %in% unlist(get_program(input$sp2, 7, "specialization"))), selected = NA,
                    multiple = TRUE, width = "100%"
                    )}}}),
        renderText(
            if (input$sp2 != "None") {
                if (as.numeric(get_program(input$sp2, 10, "specialization")) == 0) {NULL} else
                    {paste("Number of Credits =", get_credits(input$sp2e), "/", get_program(input$sp2, 10, "specialization"))}})
        )
    ))

```

<!------------------------------------------------------------------------------------------------->

# Semesters {data-navmenu="Your Degree"}

```{r YD/S}

timeline <- reactive({
    
    temp <- data.frame(sprintf("%.1f" ,c(0, seq(1,8.5,0.5))))
    
    if (as.character(input$yd_sem) == "FALL") {
        temp[,2] <- c("Transfer", "FALL", "WINTER", "SPRING", "SUMMER", "FALL", "WINTER", "SPRING", "SUMMER", 
                      "FALL", "WINTER", "SPRING", "SUMMER", "FALL", "WINTER", "SPRING", "SUMMER")
        temp[,3] <- c(0, as.numeric(input$yd_yr), as.numeric(input$yd_yr), as.numeric(input$yd_yr)+1, as.numeric(input$yd_yr)+1, as.numeric(input$yd_yr)+1, as.numeric(input$yd_yr)+1, as.numeric(input$yd_yr)+2, as.numeric(input$yd_yr)+2, as.numeric(input$yd_yr)+2, as.numeric(input$yd_yr)+2, as.numeric(input$yd_yr)+3, as.numeric(input$yd_yr)+3, as.numeric(input$yd_yr)+3, as.numeric(input$yd_yr)+3, as.numeric(input$yd_yr)+4, as.numeric(input$yd_yr)+4)} else {
        temp[,2] <- c("Transfer", "SPRING", "SUMMER", "FALL", "WINTER", "SPRING", "SUMMER", "FALL", "WINTER", 
                      "SPRING", "SUMMER", "FALL", "WINTER", "SPRING", "SUMMER", "FALL", "WINTER")
        temp[,3] <- c(0, as.numeric(input$yd_yr), as.numeric(input$yd_yr), as.numeric(input$yd_yr), as.numeric(input$yd_yr), as.numeric(input$yd_yr)+1, as.numeric(input$yd_yr)+1, as.numeric(input$yd_yr)+1, as.numeric(input$yd_yr)+1, as.numeric(input$yd_yr)+2, as.numeric(input$yd_yr)+2, as.numeric(input$yd_yr)+2, as.numeric(input$yd_yr)+2, as.numeric(input$yd_yr)+3, as.numeric(input$yd_yr)+3, as.numeric(input$yd_yr)+3, as.numeric(input$yd_yr)+3)
    }
    
    temp[,4] <- paste("Semester", temp[,1], "-", temp[,3], temp[,2])
    
    for (i in 2:17) {
        if (temp[i,3] < as.numeric(year(Sys.Date()))) {temp[i,5] <- "Complete"} else
        if (temp[i,3] == as.numeric(year(Sys.Date())) & 
            as.numeric(month(Sys.Date())) %in% get(temp[i,2])) {temp[i,5] <- "Current"} else 
        {temp[i,5] <- "incomplete"}
    }
    
    temp[1,5] <- "Complete"
    
    return(temp)
})
  
```

## column {.sidebar data-width="300"}

### Select Semester

```{r YD/S/Select}

renderUI({verticalLayout(column(
    12,
    lapply(1:16, function(i) {checkboxInput(
        inputId = paste0("s", i, "_checkbox"), 
        label = as.character(timeline()[i+1,4]), 
        value = FALSE)
        }), br(),
    actionButton(inputId = "deselect_yd_s_select", "Deselect all", width = "100%"), br(), br(),
    actionButton(inputId = "select_yd_s_select", "Select all", width = "100%")
))})

observeEvent(input$deselect_yd_s_select, {for (i in 1:16) {updateCheckboxInput(inputId = paste0("s", i, "_checkbox"), value = FALSE)}})

observeEvent(input$select_yd_s_select, {for (i in 1:16) {updateCheckboxInput(inputId = paste0("s", i, "_checkbox"), value = TRUE)}})

```

## column {data-width="400"}

### Edit Semester Details

```{r YD/S/Edit}

# functions whcih allow updates in table to update dataframe (idk how they work)
ediTable <- function(id, ...) {
    ns <- NS(id)
    rHandsontableOutput(outputId = ns("hot"), ...)
}

ediTable_server <- function(id, rd, ...) {
        moduleServer(id,
                     function(input, output, session) {
                         output$hot <- renderRHandsontable({
                             temp <- isolate(rd())
                             rhandsontable(
                                 temp,
                                 stretchH = "all",
                                 colHeaders = c("Course no", "Course", "Grade"),
                                 rowHeaders = NULL,
                                 ...) %>%
                                 hot_cols(valign = "htMiddle", halign = "htCenter") %>%
                                 hot_col("Course no", readOnly = TRUE) %>%
                                 hot_rows(rowHeights = 30) 
                             })
                         observeEvent(input$hot, {
                             temp <- rhandsontable::hot_to_r(input$hot)
                             rd(temp)
})})}

s1.0 <-  reactiveVal(data.frame(
    no = rep("Semester 1.0", each=7), 
    courses = factor("None", levels = c("None",unique(courses[,2])), ordered = TRUE),
    grades = factor("None", levels = c("None", grades[,1]), ordered = TRUE)
))

ediTable_server(id = "s1.0_GUI", rd = s1.0)

s1.5 <-  reactiveVal(data.frame(
    no = rep("Semester 1.5", each=3),
    courses = factor("None", levels = c("None",unique(courses[,2])), ordered = TRUE),
    grades = factor("None", levels = c("None", grades[,1]), ordered = TRUE)
))

ediTable_server(id = "s1.5_GUI", rd = s1.5)

s2.0 <-  reactiveVal(data.frame(
    no = rep("Semester 2.0", each=7),
    courses = factor("None", levels = c("None",unique(courses[,2])), ordered = TRUE),
    grades = factor("None", levels = c("None", grades[,1]), ordered = TRUE)
))

ediTable_server(id = "s2.0_GUI", rd = s2.0)

s2.5 <-  reactiveVal(data.frame(
    no = rep("Semester 2.5", each=3),
    courses = factor("None", levels = c("None",unique(courses[,2])), ordered = TRUE),
    grades = factor("None", levels = c("None", grades[,1]), ordered = TRUE)
))

ediTable_server(id = "s2.5_GUI", rd = s2.5)

s3.0 <-  reactiveVal(data.frame(
    no = rep("Semester 3.0", each=7),
    courses = factor("None", levels = c("None",unique(courses[,2])), ordered = TRUE),
    grades = factor("None", levels = c("None", grades[,1]), ordered = TRUE)
))

ediTable_server(id = "s3.0_GUI", rd = s3.0)

s3.5 <-  reactiveVal(data.frame(
    no = rep("Semester 3.5", each=3),
    courses = factor("None", levels = c("None",unique(courses[,2])), ordered = TRUE),
    grades = factor("None", levels = c("None", grades[,1]), ordered = TRUE)
))

ediTable_server(id = "s3.5_GUI", rd = s3.5)

s4.0 <-  reactiveVal(data.frame(
    no = rep("Semester 4.0", each=7),
    courses = factor("None", levels = c("None",unique(courses[,2])), ordered = TRUE),
    grades = factor("None", levels = c("None", grades[,1]), ordered = TRUE)
))

ediTable_server(id = "s4.0_GUI", rd = s4.0)

s4.5 <-  reactiveVal(data.frame(
    no = rep("Semester 4.5", each=3),
    courses = factor("None", levels = c("None",unique(courses[,2])), ordered = TRUE),
    grades = factor("None", levels = c("None", grades[,1]), ordered = TRUE)
))

ediTable_server(id = "s4.5_GUI", rd = s4.5)

s5.0 <-  reactiveVal(data.frame(
    no = rep("Semester 5.0", each=7),
    courses = factor("None", levels = c("None",unique(courses[,2])), ordered = TRUE),
    grades = factor("None", levels = c("None", grades[,1]), ordered = TRUE)
))

ediTable_server(id = "s5.0_GUI", rd = s5.0)

s5.5 <-  reactiveVal(data.frame(
    no = rep("Semester 5.5", each=3),
    courses = factor("None", levels = c("None",unique(courses[,2])), ordered = TRUE),
    grades = factor("None", levels = c("None", grades[,1]), ordered = TRUE)
))

ediTable_server(id = "s5.5_GUI", rd = s5.5)

s6.0 <-  reactiveVal(data.frame(
    no = rep("Semester 6.0", each=7),
    courses = factor("None", levels = c("None",unique(courses[,2])), ordered = TRUE),
    grades = factor("None", levels = c("None", grades[,1]), ordered = TRUE)
))

ediTable_server(id = "s6.0_GUI", rd = s6.0)

s6.5 <-  reactiveVal(data.frame(
    no = rep("Semester 6.5", each=3),
    courses = factor("None", levels = c("None",unique(courses[,2])), ordered = TRUE),
    grades = factor("None", levels = c("None", grades[,1]), ordered = TRUE)
))
        
ediTable_server(id = "s6.5_GUI", rd = s6.5)

s7.0 <-  reactiveVal(data.frame(
    no = rep("Semester 7.0", each=7),
    courses = factor("None", levels = c("None",unique(courses[,2])), ordered = TRUE),
    grades = factor("None", levels = c("None", grades[,1]), ordered = TRUE)
))

ediTable_server(id = "s7.0_GUI", rd = s7.0)

s7.5 <-  reactiveVal(data.frame(
    no = rep("Semester 7.5", each=3),
    courses = factor("None", levels = c("None",unique(courses[,2])), ordered = TRUE),
    grades = factor("None", levels = c("None", grades[,1]), ordered = TRUE)
))

ediTable_server(id = "s7.5_GUI", rd = s7.5)

s8.0 <-  reactiveVal(data.frame(
    no = rep("Semester 8.0", each=7),
    courses = factor("None", levels = c("None",unique(courses[,2])), ordered = TRUE),
    grades = factor("None", levels = c("None", grades[,1]), ordered = TRUE)
))

ediTable_server(id = "s8.0_GUI", rd = s8.0)

s8.5 <-  reactiveVal(data.frame(
    no = rep("Semester 8.5", each=3),
    courses = factor("None", levels = c("None",unique(courses[,2])), ordered = TRUE),
    grades = factor("None", levels = c("None", grades[,1]), ordered = TRUE)
))

ediTable_server(id = "s8.5_GUI", rd = s8.5)

renderUI({
    req(ged())
    verticalLayout(column(
        12,
        if (input$s1_checkbox ==  TRUE) {ediTable(id = "s1.0_GUI")},
        if (input$s2_checkbox ==  TRUE) {ediTable(id = "s1.5_GUI")},
        if (input$s3_checkbox ==  TRUE) {ediTable(id = "s2.0_GUI")},
        if (input$s4_checkbox ==  TRUE) {ediTable(id = "s2.5_GUI")},
        if (input$s5_checkbox ==  TRUE) {ediTable(id = "s3.0_GUI")},
        if (input$s6_checkbox ==  TRUE) {ediTable(id = "s3.5_GUI")},
        if (input$s7_checkbox ==  TRUE) {ediTable(id = "s4.0_GUI")},
        if (input$s8_checkbox ==  TRUE) {ediTable(id = "s4.5_GUI")},
        if (input$s9_checkbox ==  TRUE) {ediTable(id = "s5.0_GUI")},
        if (input$s10_checkbox ==  TRUE) {ediTable(id = "s5.5_GUI")},
        if (input$s11_checkbox ==  TRUE) {ediTable(id = "s6.0_GUI")},
        if (input$s12_checkbox ==  TRUE) {ediTable(id = "s6.5_GUI")},
        if (input$s13_checkbox ==  TRUE) {ediTable(id = "s7.0_GUI")},
        if (input$s14_checkbox ==  TRUE) {ediTable(id = "s7.5_GUI")},
        if (input$s15_checkbox ==  TRUE) {ediTable(id = "s8.0_GUI")},
        if (input$s16_checkbox ==  TRUE) {ediTable(id = "s8.5_GUI")}
))})

```

## column {data-width="300"}

### Details {data-height=400}

In regular semesters (FALL and SPRING), students take 5 courses (maximum 17 credits). However, a student may apply for semester overload which lets them take a maximum of 7 courses (maximum 22 credits).

In non regular semesters (SUMMER and WINTER), students take up to 2 courses (maximum 8 credits). However, a student may apply for semester overload which lets them take a maximum of 3 courses (maximum 10 credits)

Winter semesters are not being offered at the moment due to the disruption of the academic schedule.

Although you are likely to have as summer/winter semester after your 8th semester, you are recommended to not consider this semester when planning your degree as that semester is meant as a backup for fulfilling graduation requirements on time.

### Grading System {data-height=600}

```{r YD/S/Grades}

renderTable(na.omit(grades), striped = TRUE, hover = TRUE)

```

<!------------------------------------------------------------------------------------------------->

# Courses {data-navmenu="Your Degree"}

## column {.sidebar data-width="250"}

### Sort Courses

All of the courses that you have selected in "Details" page are shown here and have been labelled with semesters in which you have taken those courses or plan to.

If you sort by semesters, all of the courses which you have not taken yet or have not planned to take will be shown in the "No Group" section. This can act like a check-list/audit showcasing which courses are remaining.

<br>

```{r YD/C/Sort}

selectInput(inputId = "yd_sort", label = "Sort courses by", choices = c("Requirement Wise" ,"Semester Wise"))

yd_sort_no <- reactive(if (input$yd_sort == "Requirement Wise") {4} else {5})

```

## column {data-width="750"}

### {}

```{r YD/C/}

user_data <- reactive({
    
    req(ged());
    
    # convert semesters to characters for easier manipulations
    s0.0 <- as.character(input$s0.0)
    s1.0 <- as.data.frame(s1.0()); s1.5 <- as.data.frame(s1.5()); s2.0 <- as.data.frame(s2.0()); s2.5 <- as.data.frame(s2.5())
    s3.0 <- as.data.frame(s3.0()); s3.5 <- as.data.frame(s3.5()); s4.0 <- as.data.frame(s4.0()); s4.5 <- as.data.frame(s4.5())
    s5.0 <- as.data.frame(s5.0()); s5.5 <- as.data.frame(s5.5()); s6.0 <- as.data.frame(s6.0()); s6.5 <- as.data.frame(s6.5())
    s7.0 <- as.data.frame(s7.0()); s7.5 <- as.data.frame(s7.5()); s8.0 <- as.data.frame(s8.0()); s8.5 <- as.data.frame(s8.5())
    
    # get courses
    temp <- rbind(
        filter(courses[c(2:4,6)], courses$Code %in% as.character(ged())),
        filter(courses[c(2:4,6)], courses$Code %in% as.character(input$frel)),
        
        filter(courses[c(2:4,6)], courses$Code %in% unlist(get_program(as.character(input$ma1), 6, "major"))),
        filter(courses[c(2:4,6)], courses$Code %in% unlist(get_program(as.character(input$ma2), 6, "major"))),
        filter(courses[c(2:4,6)], courses$Code %in% unlist(get_program(as.character(input$mi1), 6, "minor"))),
        filter(courses[c(2:4,6)], courses$Code %in% unlist(get_program(as.character(input$mi2), 6, "minor"))),
        filter(courses[c(2:4,6)], courses$Code %in% unlist(get_program(as.character(input$sp1), 6, "specialization"))),
        filter(courses[c(2:4,6)], courses$Code %in% unlist(get_program(as.character(input$sp2), 6, "specialization"))),
        
        filter(courses[c(2:4,6)], courses$Code %in% as.character(input$ma1e)),
        filter(courses[c(2:4,6)], courses$Code %in% as.character(input$ma2e)),
        filter(courses[c(2:4,6)], courses$Code %in% as.character(input$mi1e)),
        filter(courses[c(2:4,6)], courses$Code %in% as.character(input$mi2e)),
        filter(courses[c(2:4,6)], courses$Code %in% as.character(input$sp1e)),
        filter(courses[c(2:4,6)], courses$Code %in% as.character(input$sp2e))
    )
    
    # make columns for requirement, semester, status and gpa
    temp$Requirement <- NA; temp$Semester <- NA; temp$Status <- NA; temp$GPA <- NA
    
    # assign values
    for (i in 1:nrow(temp)) {
        
        # requirement
        if (temp[i,1] %in% as.character(ged())) {temp$Requirement[i] <- "General Education"} else
        if (temp[i,1] %in% as.character(input$frel)) {temp$Requirement[i] <- "Free Elective"} else
        
        if (temp[i,1] %in% unlist(get_program(as.character(input$ma1), 6, "major"))) {temp$Requirement[i] <- paste0("Major 1 (", as.character(input$ma1), ") Core")} else
        if (temp[i,1] %in% unlist(get_program(as.character(input$ma2), 6, "major"))) {temp$Requirement[i] <- paste0("Major 2 (", as.character(input$ma2), ") Core")} else
        if (temp[i,1] %in% unlist(get_program(as.character(input$mi1), 6, "minor"))) {temp$Requirement[i] <- paste0("Minor 1 (", as.character(input$mi1), ") Core")} else
        if (temp[i,1] %in% unlist(get_program(as.character(input$mi2), 6, "minor"))) {temp$Requirement[i] <- paste0("Minor 2 (", as.character(input$mi2), ") Core")} else
        if (temp[i,1] %in% unlist(get_program(as.character(input$sp1), 6, "specialization"))) {temp$Requirement[i] <- paste0("Specialization 1 (", as.character(input$sp1), ") Core")} else
        if (temp[i,1] %in% unlist(get_program(as.character(input$sp2), 6, "specialization"))) {temp$Requirement[i] <- paste0("Specialization 2 (", as.character(input$sp2), ") Core")} else
        
        if (temp[i,1] %in% as.character(input$ma1e)) {temp$Requirement[i] <- paste0("Major 1 (", as.character(input$ma1), ") Elective")} else
        if (temp[i,1] %in% as.character(input$ma2e)) {temp$Requirement[i] <- paste0("Major 2 (", as.character(input$ma2), ") Elective")} else
        if (temp[i,1] %in% as.character(input$mi1e)) {temp$Requirement[i] <- paste0("Minor 1 (", as.character(input$mi1), ") Elective")} else
        if (temp[i,1] %in% as.character(input$mi2e)) {temp$Requirement[i] <- paste0("Minor 2 (", as.character(input$mi2), ") Elective")} else
        if (temp[i,1] %in% as.character(input$sp1e)) {temp$Requirement[i] <- paste0("Specialization 1 (", as.character(input$sp1), ") Elective")} else
        if (temp[i,1] %in% as.character(input$sp2e)) {temp$Requirement[i] <- paste0("Specialization 2 (", as.character(input$sp2), ") Elective")}
        
        # transfer semester
        if (temp[i,1] %in% s0.0) {temp[i,6:7] <- as.character(timeline()[which(timeline()[,1] == "0.0"), 4:5])}
        
        for (j in 1:8) {
            for (k in c(0,5)) {
                
                # semester and status
                if (temp[i,1] %in% get(paste0("s", j, ".", k))[,2]) {
                    temp[i,6:7] <- as.character(timeline()[which(timeline()[,1] == paste0(j, ".", k)), 4:5])}
                
                # grade
                if (temp[i,1] %in% get(paste0("s", j, ".", k))[,2]) {
                    temp[i,8] <- get(as.character(get(paste0("s", j, ".", k))[which(temp[i,1] == get(paste0("s", j, ".", k))[,2]), 3]))}
            }}
        }
    
    # final
    temp <- temp[order(temp$Requirement, temp$Code),]
    return(temp)
})

renderDT(datatable(user_data(),
                   rownames = FALSE,
                   extensions = c('Responsive', 'RowGroup', 'RowReorder'),
                   options = list(
                       rowReorder = TRUE, order = list(c(as.numeric(yd_sort_no()), 'asc')),
                       rowGroup = list(dataSrc = as.numeric(yd_sort_no())),
                       bPaginate = FALSE,
                       pageLength = 1000,
                       scrollY = "200px",
                       columnDefs = list(
                           list(className = 'dt-center', targets = c(2,4,6,7))))
))

```

<!------------------------------------------------------------------------------------------------->

# Overview {data-navmenu="Your Degree" data-orientation="rows"}

## row {data-height="150"}

### Credits

```{r YD/O/Credits}

renderValueBox(valueBox(
    value = as.numeric(user_overview()[19, ncol(user_overview())-1]),
    icon = "fa-book", color = c("#e0fbfc")
))

```

### CGPA

```{r YD/O/GPA}

renderValueBox(valueBox(
    value = user_overview()[22, ncol(user_overview())], 
    icon = "fa-pencil", color = c("#e0fbfc")
))

```

### Current Semester

```{r YD/O/Current}

renderValueBox(valueBox(
    value = timeline()[which(timeline()[,5] == "Current"), 4], 
    icon = "fa-date", color = c("#e0fbfc")
))

```

### Degree Completed (%)

```{r YD/O/Completed}

renderGauge(gauge(
    value = user_overview()[21,ncol(user_overview())-1], 
    min = 0, max = 100,
    gaugeSectors(success = c(80,100), warning = c(50,79), danger = c(0,49), 
                 color=c("#007f00", "#cc8400", "#990000"))
))

```

### Days Till Freedom

```{r YD/O/Graduation}

renderValueBox(valueBox(
    value = as.numeric(
        as.Date(paste0(as.numeric(timeline()[17,3]), "-", month(round(mean(get(timeline()[17,2])))), "-", "15"), tryFormats = c("%Y-%m-%d")) - as.Date(Sys.Date(), tryFormats = c("%Y-%m-%d"))),
    icon = "fa-clock", color = c("#e0fbfc")
))


```

## row {data-height="850"}

### Credit and GPA Distribution by Semesters and Requirements

```{r YD/O/Distribution}

user_overview <- reactive({
    
    req(ged());
    
    # template
    temp <- data.frame(ged = rep(NA, 22), ma1c = rep(NA, 22), ma1e = rep(NA, 22), ma2c = rep(NA, 22), ma2e = rep(NA, 22), mi1c = rep(NA, 22), mi1e = rep(NA, 22), mi2c = rep(NA, 22), mi2e = rep(NA, 22), sp1c = rep(NA, 22), sp1e = rep(NA, 22), sp2c = rep(NA, 22), sp2e = rep(NA, 22), frel = rep(NA, 22), total = rep(NA, 22), gpa = rep(NA, 22))
    
    # col and row names
    colnames(temp) <- c("General Education", 
                        paste0("Major 1 (", as.character(input$ma1), ") Core"), paste0("Major 1 (", as.character(input$ma1), ") Elective"), 
                        paste0("Major 2 (", as.character(input$ma2), ") Core"), paste0("Major 2 (", as.character(input$ma2), ") Elective"), 
                        paste0("Minor 1 (", as.character(input$mi1), ") Core"), paste0("Minor 1 (", as.character(input$mi1), ") Elective"), 
                        paste0("Minor 2 (", as.character(input$mi2), ") Core"), paste0("Minor 2 (", as.character(input$mi2), ") Elective"), 
                        paste0("Specialization 1 (", as.character(input$sp1), ") Core"), paste0("Specialization 1 (", as.character(input$sp1), ") Elective"), 
                        paste0("Specialization 2 (", as.character(input$sp2), ") Core"), paste0("Specialization 2 (", as.character(input$sp2), ") Elective"),
                        "Free Elective", "Total", "CGPA")
    
    rownames(temp) <- c("Required", as.character(timeline()[,4]), "Total", "Remaining", "Percentage (%)","CGPA")
    
    # assign requirement for each row
    temp[1,1] <- "47"
    
    temp[1,2:3] <- if (as.character(input$ma1) != "None") {as.character(get_program(as.character(input$ma1), 9:10, "major"))} else {NA}
    temp[1,4:5] <- if (as.character(input$ma2) != "None") {as.character(get_program(as.character(input$ma2), 9:10, "major"))} else {NA}
    
    temp[1,6:7] <- if (as.character(input$mi1) != "None") {as.character(get_program(as.character(input$mi1), 9:10, "minor"))} else {NA}
    temp[1,8:9] <- if (as.character(input$mi2) != "None") {as.character(get_program(as.character(input$mi2), 9:10, "minor"))} else {NA}
    
    temp[1,10:11] <- if (as.character(input$sp1) != "None") {as.character(get_program(as.character(input$sp1), 9:10, "specialization"))} else {NA}
    temp[1,12:13] <- if (as.character(input$sp2) != "None") {as.character(get_program(as.character(input$sp2), 9:10, "specialization"))} else {NA}
    
    temp[1,14] <- "0"
    
    temp[1,15] <- if (sum(as.numeric(temp[1,1:13]), na.rm = TRUE) > 124) {as.character(sum(as.numeric(temp[1,1:13]), na.rm = TRUE))} else {"124"}
    
    temp[1,16] <- "2.0"
    
    # assign credits for each element and gpa for each semester and requirement
    for (i in 1:14) {
        for (j in 1:17) {
            
            # credits
            temp1 <- user_data() %>%
                filter(Status == "Complete", Requirement == colnames(temp[i]), Semester == rownames(temp[j+1,])) %>%
                summarize(sum = sum(as.numeric(Credits), na.rm = TRUE))
            temp[j+1,i] <- as.character(temp1$sum)
            
            # gpa (req wise)
            temp2 <- user_data() %>%
                filter(Status == "Complete", Requirement == colnames(temp[i])) %>%
                mutate(points = as.numeric(GPA) * as.numeric(Credits)) %>%
                summarize(gpa = sum(as.numeric(points), na.rm = TRUE) / sum(as.numeric(Credits)))
            temp[22,i] <- as.character(round(temp2$gpa,2))
            
            # gpa (sem wise)
            temp3 <- user_data() %>%
                filter(Status == "Complete", Semester == rownames(temp[j+1,])) %>%
                mutate(points = as.numeric(GPA) * as.numeric(Credits)) %>%
                summarize(gpa = sum(as.numeric(points), na.rm = TRUE)/ sum(as.numeric(Credits)))
            temp[j+1,16] <- as.character(round(temp3$gpa,2))
            
     }}
    
    # assign total credits for each semester (row wise)
    for (i in 2:19) {temp[i, 15] <- sum(as.numeric(temp[i, 1:14]))}
    
    # assign total credits, remaining credits and percentage for each requirement (col wise)
    for (i in 1:15) {
        temp[19,i] <- sum(as.numeric(temp[2:18, i]), na.rm = TRUE)
        temp[20,i] <- (as.numeric(temp[1,i]) - as.numeric(temp[19,i]))
        temp[21,i] <- round(as.numeric(temp[19,i]) / as.numeric(temp[1,i]) * 100, 2)
    }
    
    # fill total gpa
    if(!is.nan(temp[16,3])) temp[22,16] <- round(mean(as.numeric(temp[3:18, 16]), na.rm = TRUE),2)
    
    # assign misc values
    temp[2, 16] <- "T" # gpa for transfer with "T
    temp[20:21, 14] <- "-" # remaining and % completed with "-" for free electives
    temp[19:21, 16] <- "-" # total, remaining and % completed with "-" for gpa
    temp[22,15] <- "-" # total with "-" for gpa
    
    # final result
    temp <- temp[,!is.na(temp[1,]), drop = F]
    return(temp)
})

eventReactive(input$import_multiple, {user_overview()})

renderTable(user_overview(), rownames = TRUE, striped = TRUE, hover = TRUE)

```

<!------------------------------------------------------------------------------------------------->
