---
title: "eX - Course Catalog (2022-2023)"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    theme: yeti
    source_code: embed
runtime: shiny
---

<!--
Github repo: https://github.com/rafaefarrukh/EmpowerX 
Read README.md for details such as code notation and data files.
-->

```{r Setup}

# Libraries ----
library(flexdashboard); library(shiny); library(shinyWidgets); library(tidyverse); library(DT)

# Data ----
courses <- read.csv("Data/courses_22.csv"); names(courses) <- c("Department", "Code", "Title", "Credits", "Details", "Prerequisite", "Crosslisted Code")
programs <- read.csv("Data/programs_22.csv"); names(programs) <- c("Program", "nature", "Details", "Requirements", "Course Categories", "Core Courses", "Elective Courses", "Total Credits", "Core Credits", "Elective Credits", "Total Courses", "Core Courses", "Elective Courses")


# Functions ----

## Extract info from "programs" based on program name and nature

get_program <- function(input, output, nature) {
    
    # input = name of program
    # output = {1,2,3...13}; each number represents column of program and the info in it
    # nature = {degree, major, minor, specialization, certification}
    
    temp <- data.frame(str_split(as.character(
        filter(programs[output], programs[1] == input, programs[2] == nature)), "\n"))
    
    names(temp) <- paste0(names(programs[output]))
    
    return(temp)
}

```

<!------------------------------------------------------------------------------------------------->

# Degree Details {.tabset}

```{r UP/DD}

tags$iframe(style="height:100%; width:100%; scrolling=yes", src="Data/degree_details.pdf")

```

<!------------------------------------------------------------------------------------------------->

# Search Courses

## column {.sidebar data-width="250"}

### Filter

Select the departments whose courses you want to see. Similarly, select the credits to view courses of those credits

If you want to search using a keyword, use the search bar on the top right of the table. 

<br>

```{r UP/SC/Filter}

pickerInput(
    inputId = "dept", label = "Department", 
    choices = sort(unique(courses[,1])),
    selected = sort(unique(courses[,1])),
    options = pickerOptions(actionsBox = TRUE, selectedTextFormat = "count > 3"),
    multiple = TRUE, width = "100%"
)

br()

pickerInput(
    inputId = "cr", label = "Credits",
    choices = c("x", sort(as.numeric(unique(courses[,4])))),
    selected = c("x", sort(as.numeric(unique(courses[,4])))),
    options = pickerOptions(actionsBox = TRUE, selectedTextFormat = "count > 3"),
    multiple = TRUE, width = "100%"
)

```

## column {data-width="750"}

### {}

```{r UP/SC/}

renderDT(datatable(
    courses %>% filter(courses[,1] %in% input$dept, courses[,4] %in% input$cr),
    rownames = FALSE, 
    extensions = 'Responsive',
    options = list(
        pageLength = "100",
        scrollY = "200px",
        columnDefs = list(
            list(width = '5pc', targets = c(0,3)),
            list(width = '7pc', targets = c(1,5,6)),
            list(width = '10pc', targets = c(2)),
            list(width = '64pc', targets = c(0)),
            list(className = 'dt-center', targets = c(0,1,3,6))))) %>%
        formatStyle(c('Department','Code'), fontWeight = 'bold')
)

```

<!------------------------------------------------------------------------------------------------->

# Search Programs

## column {.sidebar data-width="250"}

### Search

Choose a program below to see its details.

Note that only one program will be showed at a time.

<br>

```{r UP/SP/Search}

selectInput(
    inputId = "dg", label = "Degrees",
    choices = c("None", sort(programs[which(programs[,2] == "degree"),1])), selected = "None"
)

selectInput(
    inputId = "ma", label = "Majors",
    choices = c("None", sort(programs[which(programs[,2] == "major"),1])), selected = "None"
)

selectInput(
    inputId = "mi", label = "Minors",
    choices = c("None", sort(programs[which(programs[,2] == "minor"),1])), selected = "None"
)

selectInput(
    inputId = "sp", label = "Specializations",
    choices = c("None", sort(programs[which(programs[,2] == "specialization"),1])), selected = "None"
)

selectInput(
    inputId = "ct", label = "Certifications",
    choices = c("None", sort(programs[which(programs[,2] == "certification"),1])), selected = "None"
)

actionButton(inputId = "deselect_up_sp_search", label = "Reset", width = "100%")

observeEvent(input$deselect_up_sp_search, {
    updateSelectInput(inputId = "dg", selected = "None")
    updateSelectInput(inputId = "ma", selected = "None")
    updateSelectInput(inputId = "mi", selected = "None")
    updateSelectInput(inputId = "sp", selected = "None")
    updateSelectInput(inputId = "ct", selected = "None")
})

```

## column {data-width="350"}

### Details {data-height="450"}

```{r UP/SP/Details}

renderTable(
    if (input$dg != "None") {get_program(input$dg, 3, "degree")} else
    if (input$ma != "None") {get_program(input$ma, 3, "major")} else
    if (input$mi != "None") {get_program(input$mi, 3, "minor")} else
    if (input$sp != "None") {get_program(input$sp, 3, "specialization")} else
    if (input$ct != "None") {get_program(input$ct, 3, "certification")},
    colnames = FALSE, rownames = FALSE, striped = TRUE, hover = TRUE
)

```

### Requirements {data-height="450"}

```{r UP/SP/Requirements}

renderTable(
    if (input$dg != "None") {get_program(input$dg, 4, "degree")} else
    if (input$ma != "None") {get_program(input$ma, 4, "major")} else
    if (input$mi != "None") {get_program(input$mi, 4, "minor")} else
    if (input$sp != "None") {get_program(input$sp, 4, "specialization")} else
    if (input$ct != "None") {get_program(input$ct, 4, "certification")},
    colnames = FALSE, rownames = FALSE, striped = TRUE, hover = TRUE
)

```

### Credits and Courses {data-height="100"}

```{r UP/SP/Credits_and_Courses}

renderTable(
    if (input$dg != "None") {get_program(input$dg, 8:13, "degree")} else
    if (input$ma != "None") {get_program(input$ma, 8:13, "major")} else
    if (input$mi != "None") {get_program(input$mi, 8:13, "minor")} else
    if (input$sp != "None") {get_program(input$sp, 8:13, "specialization")} else
    if (input$ct != "None") {get_program(input$ct, 8:13, "certification")},
    rownames = FALSE, striped = TRUE, hover = TRUE
)

```

## column {.tabset data-width="350"}

### Core Courses

```{r UP/SP/Core}

renderTable(
    if (input$dg != "None") {filter(courses[c(2:4,6:7)], courses$Code %in% unlist(get_program(input$dg, 6, "degree")))} else
    if (input$ma != "None") {filter(courses[c(2:4,6:7)], courses$Code %in% unlist(get_program(input$ma, 6, "major")))} else
    if (input$mi != "None") {filter(courses[c(2:4,6:7)], courses$Code %in% unlist(get_program(input$mi, 6, "minor")))} else
    if (input$sp != "None") {filter(courses[c(2:4,6:7)], courses$Code %in% unlist(get_program(input$sp, 6, "specialization")))} else
    if (input$ct != "None") {filter(courses[c(2:4,6:7)], courses$Code %in% unlist(get_program(input$ct, 6, "certification")))},
    rownames = FALSE, striped = TRUE, hover = TRUE
)

```

### Elective Courses

```{r UP/SP/Elective}

renderTable(
    if (input$dg != "None") {filter(courses[c(2:4,6:7)], courses$Code %in% unlist(get_program(input$dg, 7, "degree")))} else
    if (input$ma != "None") {filter(courses[c(2:4,6:7)], courses$Code %in% unlist(get_program(input$ma, 7, "major")))} else
    if (input$mi != "None") {filter(courses[c(2:4,6:7)], courses$Code %in% unlist(get_program(input$mi, 7, "minor")))} else
    if (input$sp != "None") {filter(courses[c(2:4,6:7)], courses$Code %in% unlist(get_program(input$sp, 7, "specialization")))} else
    if (input$ct != "None") {filter(courses[c(2:4,6:7)], courses$Code %in% unlist(get_program(input$ct, 7, "certification")))},
    rownames = FALSE, striped = TRUE, hover = TRUE
)

```

### Course Categories (if required)

```{r UP/SP/Course_Categories}

renderTable(
    if (input$dg != "None") {get_program(input$dg, 5, "degree")} else
    if (input$ma != "None") {get_program(input$ma, 5, "major")} else
    if (input$mi != "None") {get_program(input$mi, 5, "minor")} else
    if (input$sp != "None") {get_program(input$sp, 5, "specialization")} else
    if (input$ct != "None") {get_program(input$ct, 5, "certification")},
    colnames = FALSE, rownames = FALSE, striped = TRUE, hover = TRUE
)

```

<!------------------------------------------------------------------------------------------------->