---
title: "eX - Check List"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    theme: yeti
    source_code: embed
runtime: shiny
---

<!--
Github repo: https://github.com/rafaefarrukh/EmpowerX 
Read README.md for details such as code notation and data files.
-->

```{r Setup}

# Libraries ----
library(flexdashboard); library(shiny); library(tidyverse); library(DT);

# Data ----

## Courses
courses <- read.csv("Data/courses_22.csv")
names(courses) <- c("Department", "Code", "Title", "Credits", "Details", "Prerequisite", "Crosslisted Code")

## Programs
programs <- read.csv("Data/programs_22.csv")
names(programs) <- c("Program", "nature", "Details", "Requirements", "Course Categories", "Core Courses", "Elective Courses", "Total Credits", "Core Credits", "Elective Credits", "Total Courses", "Core Courses", "Elective Courses")

# Functions ----

## Extract info from "programs" based on program name and nature
## Used in: UP/SP/Details UP/SP/Requirements UP/SP/Credits_and_Courses UP/SP/Core UP/SP/Elective UP/SP/Course_Categories YD/C/Courses YD/O/Distribution

get_program <- function(input, output, nature) {
        
    # input = name of program
    # output = {1,2,3...13}; each number represents column of program and the info in it
    # nature = {degree, major, minor, specialization, certification}
    
    temp <- data.frame(str_split(as.character(
        filter(programs[output], programs[1] == input, programs[2] == nature)), "\n"))
    
    names(temp) <- paste0(names(programs[output]))
    
    return(temp)
}

## Calculate total number of credits based on course codes
## Used in: YD/D/General YD/D/Courses YD/D/Transfer YD/D/Elective YD/S/Edit
get_credits <- function(input) {sum(as.numeric(unlist(filter(courses[4], courses$Code %in% input))), na.rm = TRUE)}

```

<!------------------------------------------------------------------------------------------------->

# Details

## column {data-width="250"}

### Export and Import Data

```{r YD/D/Export_Import}

renderUI(verticalLayout(
    renderUI(downloadButton(outputId = "export", label = "Export your data")), br(),
    fileInput(inputId = "import", label = "", accept = ".csv", width = "100%", buttonLabel = "Import"),
    actionButton(inputId = "import_multiple", label = "Click after importing data to refresh EmpowerX", width = "100%")
    ))

# export
output$export <- downloadHandler(
    filename = function() {paste0('your_degree-', Sys.Date(), '.csv', sep='')}, 
    content = function(con) {write.csv(as.data.frame(export()), con, row.names = FALSE)})

export <- reactive({
    
    temp <- data.frame(rep(NA, 20))
    
    temp[1:6, 2] <- as.character(c(input$ma1, input$ma2, input$mi1, input$mi2, input$sp1, input$sp2))
    
    temp[,3] <- c(as.character(input$ma1e), rep(NA, 20 - length(as.character(input$ma1e))))
    temp[,4] <- c(as.character(input$ma2e), rep(NA, 20 - length(as.character(input$ma2e))))
    temp[,5] <- c(as.character(input$mi1e), rep(NA, 20 - length(as.character(input$mi1e))))
    temp[,6] <- c(as.character(input$mi2e), rep(NA, 20 - length(as.character(input$mi2e))))
    temp[,7] <- c(as.character(input$sp1e), rep(NA, 20 - length(as.character(input$sp1e))))
    temp[,8] <- c(as.character(input$sp2e), rep(NA, 20 - length(as.character(input$sp2e))))
    
    temp[,9] <- c(as.character(input$ged1), rep(NA, 20 - length(as.character(input$ged1))))
    temp[1:2,10] <- c(as.character(input$ged2), rep(NA, 2 - length(as.character(input$ged2))))
    temp[3:4,10] <- c(as.character(input$ged3), rep(NA, 2 - length(as.character(input$ged3))))
    temp[5:6,10] <- c(as.character(input$ged4), rep(NA, 2 - length(as.character(input$ged4))))
    temp[7,10] <- c(as.character(input$ged5))
    
    temp[,11] <- c(as.character(input$frel), rep(NA, 20 - length(as.character(input$frel))))
    
    temp[,12] <- c(as.character(input$s0.0), rep(NA, 20 - length(as.character(input$s0.0))))
    
    return(temp)
})

# import
import <- reactive(export())

import <- eventReactive(input$import, {read.csv(input$import$datapath)})

observeEvent(input$import, {
    
    updateSelectInput(inputId = "ma1", selected = as.character(import()[1,2]))
    updateSelectInput(inputId = "ma2", selected = as.character(import()[2,2]))
    updateSelectInput(inputId = "mi1", selected = as.character(import()[3,2]))
    updateSelectInput(inputId = "mi2", selected = as.character(import()[4,2]))
    updateSelectInput(inputId = "sp1", selected = as.character(import()[5,2]))
    updateSelectInput(inputId = "sp2", selected = as.character(import()[6,2]))
    
    updateSelectInput(inputId = "ged2", selected = as.character(import()[1:2,10]))
    updateSelectInput(inputId = "ged3", selected = as.character(import()[3:4,10]))
    updateSelectInput(inputId = "ged4", selected = as.character(import()[5:6,10]))
    updateSelectInput(inputId = "ged5", selected = as.character(import()[7,10]))

})

observeEvent(input$import_multiple, {
    
    updateSelectInput(inputId = "ma1e", selected = as.character(import()[,3]))
    updateSelectInput(inputId = "ma2e", selected = as.character(import()[,4]))
    updateSelectInput(inputId = "mi1e", selected = as.character(import()[,5]))
    updateSelectInput(inputId = "mi2e", selected = as.character(import()[,6]))
    updateSelectInput(inputId = "sp1e", selected = as.character(import()[,7]))
    updateSelectInput(inputId = "sp2e", selected = as.character(import()[,8]))
    
    updateSelectInput(inputId = "ged1", selected = as.character(import()[,9]))
    updateSelectInput(inputId = "frel", selected = as.character(import()[,11]))
    updateSelectInput(inputId = "s0.0", selected = as.character(import()[,12]))
    
})

```

### Total Credits

```{r D/Credits}

renderValueBox(valueBox(
    value = get_credits(input$s0.0) + get_credits(ged()) + get_credits(input$ma1e) + get_credits(input$ma2e) + get_credits(input$mi1e) + get_credits(input$mi2e) + get_credits(input$sp1e) + get_credits(input$sp2e) + get_credits(input$frel),
    icon = "fa-book", color = c("#e0fbfc")
))

```

### About {data-height="1000"}

empowerX is an unofficial collection of services meant to make degree planning easier for undergraduate students of FCCU. All source files can be found here: https://github.com/rafaefarrukh/EmpowerX

**Other Services**

Course Catalog: Search courses and programs offered by FCCU. https://empowerx.shinyapps.io/CourseCatalog/

Time Table: Easily view coursed offered by FCCU each semester and generate a time table for your semester. https://empowerx.shinyapps.io/TimeTable/

Checklist: Generate a checklist of courses you need to study to graduate (can act as a degree audit as well). https://empowerx.shinyapps.io/Checklist/


## column {data-width="250"}

### Degree Details

```{r YD/D/Details}

selectInput(
    inputId = "ma1", label = "Major 1",
    choices = c("None", sort(programs[which(programs[,2] == "major"),1])), selected = "None",
    width = "100%"
)

selectInput(
    inputId = "ma2", label = "Major 2",
    choices = c("None", sort(programs[which(programs[,2] == "major"),1])), selected = "None",
    width = "100%"
)

selectInput(
    inputId = "mi1", label = "Minor 1", 
    choices = c("None", sort(programs[which(programs[,2] == "minor"),1])), selected = "None",
    width = "100%"
)

selectInput(
    inputId = "mi2", label = "Minor 2",
    choices = c("None", sort(programs[which(programs[,2] == "minor"),1])), selected = "None",
    width = "100%"
)

selectInput(
    inputId = "sp1", label = "Specialization 1",
    choices = c("None", sort(programs[which(programs[,2] == "specialization"),1])), selected = "None",
    width = "100%"
)

selectInput(
    inputId = "sp2", label = "Specialization 2",
    choices = c("None", sort(programs[which(programs[,2] == "specialization"),1])), selected = "None",
    width = "100%"
)

actionButton(inputId = "deselect_yd_d_details", label = "Reset")

observeEvent(input$deselect_yd_d_details, {
    updateVarSelectInput(inputId = "ma1", selected = "None")
    updateVarSelectInput(inputId = "ma2", selected = "None")
    updateVarSelectInput(inputId = "mi1", selected = "None")
    updateVarSelectInput(inputId = "mi2", selected = "None")
    updateVarSelectInput(inputId = "sp1", selected = "None")
    updateVarSelectInput(inputId = "sp2", selected = "None")
})

```

## column {data-width="250"}

###  {data-height="700"}

```{r YD/D/General}

renderUI(verticalLayout(
    renderText("Choose General Education Courses"), br(),

    selectizeInput(
        inputId = "ged1", label = "Compulsory Courses",
        options = list(maxItems = 8), 
        choices = sort(unique(courses[,2])),
        selected = c("UNIV 100", "WRCM 101", "WRCM 102", "PKST 101", "ISLM 101", "URDU 101", "MATH 100", "CSCS 100"),
        multiple = TRUE, width = "100%"
        ),
    
    selectizeInput(
        inputId = "ged2", label = "2 Science Lab Courses",
        options = list(maxItems = 2),
        choices = arrange(filter(courses[2], 
                                 courses$Department %in% c("BIOL", "CHEM", "PHYS"),
                                 courses$Credits %in% c(4))),
        selected = NA, 
        multiple = TRUE, width = "100%"
        ),
    
    selectizeInput(
        inputId = "ged3", label = "2 Social Science Courses",
        options = list(maxItems = 2),
        choices = arrange(filter(courses[2], 
                                 courses$Department %in% c("BUSN", "ECON", "EDUC", "GEOG", "PLSC", "PSYC", "SOCL", "CRIM"),
                                 courses$Credits %in% c(3,4))),
        selected = NA, 
        multiple = TRUE, width = "100%"
        ),
    
    selectizeInput(
        inputId = "ged4", label = "2 Humanities Courses",
        options = list(maxItems = 2),
        choices = arrange(filter(courses[2], 
                                 courses$Department %in% c("ENGL", "LING", "HIST", "MCOM", "PHIL", "ISLM", "CRST", "URDU", "FREN", "GRMN", "KORN", "CHIN"),
                                 courses$Credits %in% c(3,4))),
        selected = NA, 
        multiple = TRUE, width = "100%"
    ),
    
    selectizeInput(
        inputId = "ged5", label = "1 Course from any Domain",
        options = list(maxItems = 1),
        choices = c("PHIL 221", arrange(filter(courses[2], 
                                               courses$Department %in% c("CSCS", "COMP", "MATH", "STAT", "BIOL", "BIOT", "ENVR", "CHEM", "PHYS"),
                                               courses$Credits %in% c(3,4)))),
        selected = NA, 
        multiple = FALSE,  width = "100%"
    ),
    
    renderText(paste("Number of Credits = ", get_credits(ged()))), br(), hr(), br(),
    renderText("Choose Transfer Courses"),
    
    selectInput(inputId = "s0.0", label = "", choices = sort(unique(courses[,2])), selected = NA, multiple = TRUE,  width = "100%"),
    
    renderText(paste("Number of Credits = ", get_credits(input$s0.0)))

))

ged <- reactive(rbind(input$ged1, input$ged2, input$ged3, input$ged4, input$ged5))

```

## column {data-width="250"}

### Choose Free Elective Courses {data-height="300"}

```{r YD/D/Elective}

renderUI(verticalLayout(
    
    selectInput(inputId = "frel", label = "Free Electives", choices = sort(unique(courses[,2])), selected = NA, multiple = TRUE, width = "100%"),
    
    renderText(paste("Number of Credits = ", get_credits(input$frel))), br(), hr(), br(),
    
    # ma1e
    conditionalPanel(
        condition = "input.ma1 != 'None'",
        renderUI({
            if (input$ma1 != "None") {if (as.numeric(get_program(input$ma1, 10, "major")) == 0) {"No Elective Courses for Major 1"} else {
                selectInput(
                    inputId = "ma1e", label = "Major 1 Elective Courses",
                    choices = filter(courses[2], courses$Code %in% unlist(get_program(input$ma1, 7, "major"))), selected = NA,
                    multiple = TRUE, width = "100%"
                    )}}}),
        renderText(
            if (input$ma1 != "None") {
                if (as.numeric(get_program(input$ma1, 10, "major")) == 0) {NULL} else
                    {paste("Number of Credits =", get_credits(input$ma1e), "/", get_program(input$ma1, 10, "major"))}}), br()
        ),
    
    # ma2e
    conditionalPanel(
        condition = "input.ma2 != 'None'",
        renderUI({
            if (input$ma2 != "None") {if (as.numeric(get_program(input$ma2, 10, "major")) == 0) {"No Elective Courses for Major 2"} else {
                selectInput(
                    inputId = "ma2e", label = "Major 2 Elective Courses",
                    choices = filter(courses[2], courses$Code %in% unlist(get_program(input$ma2, 7, "major"))), selected = NA,
                    multiple = TRUE, width = "100%"
                    )}}}),
        renderText(
            if (input$ma2 != "None") {
                if (as.numeric(get_program(input$ma2, 10, "major")) == 0) {NULL} else
                    {paste("Number of Credits =", get_credits(input$ma2e), "/", get_program(input$ma2, 10, "major"))}}), br()
        ),
    
    # mi1e
    conditionalPanel(
        condition = "input.mi1 != 'None'",
        renderUI({
            if (input$mi1 != "None") {if (as.numeric(get_program(input$mi1, 10, "minor")) == 0) {"No Elective Courses for Minor 1"} else {
                selectInput(
                    inputId = "mi1e", label = "Minor 1 Elective Courses",
                    choices = filter(courses[2], courses$Code %in% unlist(get_program(input$mi1, 7, "minor"))), selected = NA, 
                    multiple = TRUE, width = "100%"
                    )}}}),
        renderText(
            if (input$mi1 != "None") {
                if (as.numeric(get_program(input$mi1, 10, "minor")) == 0) {NULL} else
                    {paste("Number of Credits =", get_credits(input$mi1e), "/", get_program(input$mi1, 10, "minor"))}}), br()
        ),
    
    # mi2e
    conditionalPanel(
        condition = "input.mi2 != 'None'",
        renderUI({
            if (input$mi2 != "None") {if (as.numeric(get_program(input$mi2, 10, "minor")) == 0) {"No Elective Courses for Minor 1"} else {
                selectInput(
                    inputId = "mi2e", label = "Minor 2 Elective Courses", 
                    choices = filter(courses[2], courses$Code %in% unlist(get_program(input$mi2, 7, "minor"))), selected = NA,
                    multiple = TRUE, width = "100%"
                    )}}}),
        renderText(
            if (input$mi2 != "None") {
                if (as.numeric(get_program(input$mi2, 10, "minor")) == 0) {NULL} else
                    {paste("Number of Credits =", get_credits(input$mi2e), "/", get_program(input$mi2, 10, "minor"))}}), br()
        ),
    
    # sp1e
    conditionalPanel(
        condition = "input.sp1 != 'None'",
        renderUI({
            if (input$sp1 != "None") {if (as.numeric(get_program(input$sp1, 10, "specialization")) == 0)  {"No Elective Courses for Specialization 1"} else {
                selectInput(
                    inputId = "sp1e", label = "specialization 1 Elective Courses",
                    choices = filter(courses[2], courses$Code %in% unlist(get_program(input$sp1, 7, "specialization"))), selected = NA,
                    multiple = TRUE, width = "100%"
                    )}}}),
        renderText(
            if (input$sp1 != "None") {
                if (as.numeric(get_program(input$sp1, 10, "specialization")) == 0) {NULL} else
                    {paste("Number of Credits =", get_credits(input$sp1e), "/", get_program(input$sp1, 10, "specialization"))}}), br()
        ), br(),
    
    # sp2e
    conditionalPanel(
        condition = "input.sp2 != 'None'",
        renderUI({
            if (input$sp2 != "None") {if (as.numeric(get_program(input$sp2, 10, "specialization")) == 0) {"No Elective Courses for specialization 1"} else {
                selectInput(
                    inputId = "sp2e", label = "Specialization 2 Elective Courses",
                    choices = filter(courses[2], courses$Code %in% unlist(get_program(input$sp2, 7, "specialization"))), selected = NA,
                    multiple = TRUE, width = "100%"
                    )}}}),
        renderText(
            if (input$sp2 != "None") {
                if (as.numeric(get_program(input$sp2, 10, "specialization")) == 0) {NULL} else
                    {paste("Number of Credits =", get_credits(input$sp2e), "/", get_program(input$sp2, 10, "specialization"))}})
        )
    ))

```

<!------------------------------------------------------------------------------------------------->

# Courses

## column

### {}

```{r YD/C/}

user_data <- reactive({
    
    req(ged());
    
    # get courses
    temp <- rbind(
        filter(courses[c(2:4,6)], courses$Code %in% as.character(ged())),
        filter(courses[c(2:4,6)], courses$Code %in% as.character(input$frel)),
        
        filter(courses[c(2:4,6)], courses$Code %in% unlist(get_program(as.character(input$ma1), 6, "major"))),
        filter(courses[c(2:4,6)], courses$Code %in% unlist(get_program(as.character(input$ma2), 6, "major"))),
        filter(courses[c(2:4,6)], courses$Code %in% unlist(get_program(as.character(input$mi1), 6, "minor"))),
        filter(courses[c(2:4,6)], courses$Code %in% unlist(get_program(as.character(input$mi2), 6, "minor"))),
        filter(courses[c(2:4,6)], courses$Code %in% unlist(get_program(as.character(input$sp1), 6, "specialization"))),
        filter(courses[c(2:4,6)], courses$Code %in% unlist(get_program(as.character(input$sp2), 6, "specialization"))),
        
        filter(courses[c(2:4,6)], courses$Code %in% as.character(input$ma1e)),
        filter(courses[c(2:4,6)], courses$Code %in% as.character(input$ma2e)),
        filter(courses[c(2:4,6)], courses$Code %in% as.character(input$mi1e)),
        filter(courses[c(2:4,6)], courses$Code %in% as.character(input$mi2e)),
        filter(courses[c(2:4,6)], courses$Code %in% as.character(input$sp1e)),
        filter(courses[c(2:4,6)], courses$Code %in% as.character(input$sp2e))
    )
    
    # make columns for requirement
    temp$Requirement <- NA;
    
    # assign requirements
    
    ## general education
    temp[which(temp[,1] %in% as.character(ged())),5] <- "General Education"
    
    ## core courses
    temp[which(temp[,1] %in% unlist(get_program(input$ma1, 6, "major"))),5] <- paste0("Major 1 (", as.character(input$ma1), ") Core")
    temp[which(temp[,1] %in% unlist(get_program(input$ma2, 6, "major"))),5] <- paste0("Major 2 (", as.character(input$ma2), ") Core")
    temp[which(temp[,1] %in% unlist(get_program(input$mi1, 6, "minor"))),5] <- paste0("Minor 1 (", as.character(input$mi1), ") Core")
    temp[which(temp[,1] %in% unlist(get_program(input$mi2, 6, "minor"))),5] <- paste0("Minor 2 (", as.character(input$mi2), ") Core")
    temp[which(temp[,1] %in% unlist(get_program(input$sp1, 6, "specialization"))),5] <- paste0("Specialization 1 (", as.character(input$sp1), ") Core")
    temp[which(temp[,1] %in% unlist(get_program(input$sp2, 6, "specialization"))),5] <- paste0("Specialization 2 (", as.character(input$sp2), ") Core")
    
    ## elective courses
    temp[which(temp[,1] %in% as.character(input$ma1e)),5] <- paste0("Major 1 (", as.character(input$ma1), ") Elective")
    temp[which(temp[,1] %in% as.character(input$ma2e)),5] <- paste0("Major 2 (", as.character(input$ma2), ") Elective")
    temp[which(temp[,1] %in% as.character(input$mi1e)),5] <- paste0("Minor 1 (", as.character(input$mi1), ") Elective")
    temp[which(temp[,1] %in% as.character(input$mi2e)),5] <- paste0("Minor 2 (", as.character(input$mi2), ") Elective")
    temp[which(temp[,1] %in% as.character(input$sp1e)),5] <- paste0("Specialization 1 (", as.character(input$sp1), ") Elective")
    temp[which(temp[,1] %in% as.character(input$sp2e)),5] <- paste0("Specialization 2 (", as.character(input$sp2), ") Elective")
    
    ## free electives
    temp[which(temp[,1] %in% as.character(input$frel)),5] <- "Free Elective"

    # final
    temp <- temp[order(temp$Requirement, temp$Code),]
    return(temp)
})

renderDT(
    datatable(
        user_data(),
        rownames = FALSE,
        extensions = c('Responsive', 'RowGroup'),
        options = list(
            rowGroup = list(dataSrc = 4),
            bPaginate = FALSE,
            pageLength = 1000,
            scrollY = "200px",
            columnDefs = list(list(className = 'dt-center', targets = c(2,4)))
            )
        )
    )

```