---
title: "eX - Time Table"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    theme: yeti
    source_code: embed
runtime: shiny
---

<!--
Github repo: https://github.com/rafaefarrukh/EmpowerX 
Read README.md for details such as code notation and data files.
--> 

```{r Setup}

# Libraries ----
library(flexdashboard); library(shiny); library(shinyWidgets); library(tidyverse); library(DT); library(readxl)

# Data ----

## course lists
su <- read_xls("Data/2024SU.xls")
fa <- read_xls("Data/2024FA.xls")
sp <- read_xls("Data/2025SP.xls")
dummy <- data.frame("-", "-", "-", "-", "-", "-", "-", "-", "MTWRF", "-", "-", "-", "-", "-", "-", "-", "-", "-")

## combine
courses <- data.frame(rbind(su, fa, sp))

## data cleaning
names(courses) <- c("term", "dept", "codeOnly", "sec", "session", "title", "loc", "room", "days", "time", "instructor", "credits", "available", "offered", "date", "location", "method", "enrolled")
names(dummy) <- c("term", "dept", "codeOnly", "sec", "session", "title", "loc", "room", "days", "time", "instructor", "credits", "available", "offered", "date", "location", "method", "enrolled")

courses <- courses %>% 
  mutate(seats = paste(available, "/", offered),
         start = str_sub(time, 1, 5),
         end = str_sub(time, 9,14),
         code = paste(dept, codeOnly)) %>%
  mutate(codeOnly = NULL, session = NULL, loc = NULL, time = NULL, available = NULL, offered = NULL, date = NULL, location = NULL, method = NULL, enrolled = NULL)

dummy <- dummy %>% 
  mutate(seats = paste(available, "/", offered),
         start = str_sub(time, 1, 5),
         end = str_sub(time, 9,14),
         code = paste(dept, codeOnly)) %>%
  mutate(codeOnly = NULL, session = NULL, loc = NULL, time = NULL, available = NULL, offered = NULL, date = NULL, location = NULL, method = NULL, enrolled = NULL)

courses <- courses[,c(1,2,12,4,3,8,7,6,10,11,5,9)]
dummy <- dummy[,c(1,2,12,4,3,8,7,6,10,11,5,9)]

## factorizing columns
courses$term <- factor(courses$term)
courses$dept <- factor(courses$dept)
courses$credits <- factor(courses$credits)
courses$start <- factor(courses$start)
courses$end <- factor(courses$end)

```

<!------------------------------------------------------------------------------------------------->

# Your Time Table

## column {.sidebar data-width=300}

### How to use this service

On Search Courses page, click on the course you want to study. You can use the filters and search bar for easier navigation.

These courses will be displayed on this page.

Click on the PDF button to get a pdf file.

### About

empowerX is an unofficial collection of services meant to make degree planning easier for undergraduate students of FCCU. All source files can be found on [github](https://github.com/rafaefarrukh/EmpowerX)

**Other Services**

[Course Catalog](https://empowerx.shinyapps.io/CourseCatalog/): Search courses and programs offered by FCCU.

[Time Table](https://empowerx.shinyapps.io/TimeTable/): Easily view coursed offered by FCCU each semester and generate a time table for your semester.

[Checklist](https://empowerx.shinyapps.io/Checklist/): Generate a checklist of courses you need to study to graduate (can act as a degree audit as well).


## column {data-width=700}

### Overview {data-height=200}

```{r}

output$overview <- renderDT(
    datatable(
        selected()[,2:7],
        rownames = FALSE,
        extensions = c('Buttons'),
        options = list(
            dom = 'Bt',
            pageLength = "100",
            buttons = c('copy', 'csv', 'excel', 'pdf', 'print')
            )
        )
)

dataTableOutput("overview")

```

### Courses {data-height=800}

```{r YTT/Function}

selected <- reactive(courses[input$table_rows_selected,])

timetable <- reactive({
  
  tempM <- data.frame(day = "1", rbind(dummy[3:11],
      selected()[which(str_detect(selected()[,8], "M")),c(3:11)]))
  tempT <- data.frame(day = "2", rbind(dummy[3:11],
      selected()[which(str_detect(selected()[,8], "T")),c(3:11)]))
  tempW <- data.frame(day = "3", rbind(dummy[3:11],
      selected()[which(str_detect(selected()[,8], "W")),c(3:11)]))
  tempR <- data.frame(day = "4", rbind(dummy[3:11],
      selected()[which(str_detect(selected()[,8], "R")),c(3:11)]))
  tempF <- data.frame(day = "5", rbind(dummy[3:11],
      selected()[which(str_detect(selected()[,8], "F")),c(3:11)]))
  
  temp <- data.frame(rbind(tempM, tempT, tempW, tempR, tempF))
  temp <- arrange(temp, day, start)
  
  temp[which(temp[,1] == "1"),1] <- "Monday"
  temp[which(temp[,1] == "2"),1] <- "Tuesday"
  temp[which(temp[,1] == "3"),1] <- "Wednesday"
  temp[which(temp[,1] == "4"),1] <- "Thursday"
  temp[which(temp[,1] == "5"),1] <- "Friday"
  
  temp <- temp %>% 
    mutate(course = paste0(code, ": ", title, " (", sec, ") (", credits, ")")) %>%
    mutate(code = NULL, title = NULL, sec = NULL, credits = NULL, days = NULL)
  
  temp <- temp[,c(1,6,3,4,5,2)]
  
  names(temp) <- c("Day", "Course (section) (credits)", "Start", "End", "Room", "Instructor")
  
  temp[which(temp[,3] == "-"),2] <- "-"
  
  return(temp)

})

```

```{r YTT/UI}

tags$style(type="text/css",
         ".shiny-output-error { visibility: hidden; }",
         ".shiny-output-error:before { visibility: hidden; }"
         )

renderDT(
    datatable(
        timetable(),
        rownames = FALSE, 
        extensions = c('RowGroup', 'Buttons'),
        options = list(
            dom = 'Bfti',
            pageLength = "100",
            dom = "Bfrtip",
            buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
            columnDefs = list(
                list(width = '10pc', targets = c(0)),
                list(width = '50pc', targets = c(1)),
                list(width = '10pc', targets = c(2,3,4,5))
                )
            )
        )
    )

```

<!------------------------------------------------------------------------------------------------->

# Search Courses

## column

### {}

```{r SC}

output$table <- renderDT(datatable(
  courses,
  rownames = FALSE, 
  filter = list(position = 'top', clear = TRUE),
  options = list(
    dom = 'frtip',
    pageLength = "100",
    columnDefs = list(
      list(width = '5pc', targets = c(0,1,4,5)),
      list(width = '7pc', targets = c(2,6,7,8,9,10,11)),
      list(width = '10pc', targets = c(3)),
      list(className = 'dt-center', targets = c(0,1,2,4,5,7,8,9,10,11))))) %>%
    formatStyle(c('code', 'title'), fontWeight = 'bold')
  )

dataTableOutput("table")

```

<!------------------------------------------------------------------------------------------------->